D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-01 ootavacuous.tex
Litmus name to filename and default initialization
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

The first line identifies it as a C-language litmus test and gives it
a name.
Lines~2--5 initialize variables, in this case setting the initial
values of the global shared variables \co{x} and \co{y} to zero.
Lines~7--13 define the first thread, \co{P0()}, and lines~15--21
define the second thread, \co{P1()}.\footnote{
	The ``P'' stands for ``process'', which is \co{herd7}'s name
	for ``thread''.}
The arguments to both \co{P0()} and \co{P1()} specify which of
the global shared variables each thread may access, in this case, \co{x}
and \co{y}.
The body of each thread contains a limited subset of C++ code
(written in a slightly stilted manner to keep the load operations separate
from the rest).

>>>>

The first line identifies it as a C-language litmus test and gives it
a name, and this name identifies the litmus test's source file within
the \path{litmus} directory in the \url{https://github.com/paulmckrcu/oota}
repository.
Lines~2--5 initialize variables, in this case setting the initial
values of the global shared variables \co{x} and \co{y} to zero.
Variables that are not explicitly initialized are initialized by
default to zero.
Lines~7--13 define the first thread, \co{P0()}, and lines~15--21
define the second thread, \co{P1()}.\footnote{
	The ``P'' stands for ``process'', which is \co{herd7}'s name
	for ``thread''.}
The arguments to both \co{P0()} and \co{P1()} specify which of
the global shared variables each thread may access, in this case, \co{x}
and \co{y}.
The body of each thread contains a limited subset of C++ code
(written in a slightly stilted manner to keep the load operations separate
from the rest).
